\graphicspath{{chapters/chapter3/}}
\chapter{Literature Review}

\section{Stagnation in Ant Colony Optimization}

\subsection{Introduction}
Hvem formulerte det? Definer stagnation: er det når det ikke lages nye løsninger? Eller er det når de nylig genererte løsningene er like som den current global (reinforced) solution?

\subsection{Detecting Stagnation}
Hva er et godt mål for stagnation? 

\begin{itemize}
    \item[] \textbf{Fitness} kanskje for crude? Den sier ikke noe om hvordan løsninger som genereres, fitness verdiene som produserer følger en power curve
    \item[] \textbf{Previously generated} Similarity to previously generated solutions? krever at vi sparer veldig mange løsninger.
    \item[] \textbf{Similarity} to the current global solution? Euclidian differansen mellom global best of iteration best? matematisk tyngre.
\end{itemize}

\subsection{Preventing Stagnation}
bruk mange artikler!

%end Stagnation in Ant Colony Optimization


\section{Labor Division}

\subsection{Introduction}
hvorfor er det en god ide, hva er smart, basis in nature

\subsection{Models of Labor Division}
\begin{itemize}
    \item[] \textbf{fixed threshold function} (nevne integrated threshold function?)
    \item[] \textbf{self\@{-}reinforcement} ("gjør ant’en noe bra, prøver den å gjenta sukseen")
    \item[] \textbf{Foraging for work?} (alle er foragers, deretter alle er scouts. Varierer mellom epokene)
    \item[] \textbf{Social inhibition?}
    \item[] \textbf{extra} implementasjoner av labor division i andre fag-grener (slik som bee)?
\end{itemize}

%end Stagnation in Ant Colony Optimization


\section{Generating Realistic Test Graphs}
\begin{itemize}
    \item[] \textbf{random graphs vs realistic graphs} small world graphs are realistic. Mention who named them, and the papers that support this claim
    \item[] \textbf{power law} 
    \item[] \textbf{clustering}
\end{itemize}

%end Stagnation in Ant Colony Optimization


\section{Solving Single-Source Uncapacitated Minimum Cost Network Flow Problems}
\begin{itemize}
    \item[] \textbf{NP}When concave costs are introduced inMCNFPs, the difficulty to solve them increases and they become NP-Hard (Guisewite and Pardalos, 1991).
    \item[] \textbf{NP} with fixed-charge costs has also been proven to be NP-Hard by Hochbaum and Segev (1989). Kennington and Unger (1976), Barr et al (1981), and Palekar et al (1990) discuss the difficulty ofMCNFPs re- garding the case of fixed-charge cost functions.
    \item[] \textbf{generality} One of the main attractiveness of concave MCNFPs is that any Network Flow Problem (NFP) with general nonlinear costs can be transformed into a concaveNFP in an expanded network (Lamar, 1993) 
    \item[] \textbf{generality} capacitated and multiple sources can be transformed into uncapacitated and single-source NFPs (Wagner, 1958; Zangwill, 1968).
    \item[] \textbf{ACO solved by} (Concave Minimum Cost Network Flow Problems Solved with a Colony of Ants, 2013) and (An ant colony system-based hybrid algorithm for square root concave cost transhipment problems, 2010)
\end{itemize}

%end Stagnation in Ant Colony Optimization


\section{Related Work}
\begin{itemize}
    \item[] \textbf{hybrid functions} snakke om de som har brukt hybrid functions
    \item[] \textbf{paper} An Ant Colony Optimization Algorithm to Solve the Minimum Cost Network Flow Problem with Concave Cost Functions
    \item[] \textbf{paper}Combining Lagrangian heuristic and Ant Colony System to solve the Single Source Capacitated Facility Location Problem
    \item[] \textbf{paper} An improved ant colony optimization based algorithm for the capacitated arc routing problem
    \item[] \textbf{paper} An ant colony system-based hybrid algorithm for square root concave cost transhipment problems
\end{itemize}